|

### 2021-04-12 04-Chp-Systematic-Review.Rmd
End of day: -3686

@@

At present, no risk of bias assessment tool for Mendelian randomization studies is available. Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review were obtained from contact with the authors.

Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as part of this thesis to aid in creating standard risk-of-bias figures, and is summarized in Appendix \@ref(appendix-robvis).[@mcguinness2019]

@@

Inter- and intra-rater reliability was asssessed for a 10% subsample of records at the title and abstract screening stage. Intra-rater reliability involved a sinlge reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: @gwet2008; @wongpakaran2013]

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.

@@

@@

@@

>>>>

## Extra studies to include:

* Smeet et al. reference in the CPRD analysis

@@

At present, no risk of bias assessment tool for Mendelian randomization studies is available. Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.

Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).

Many reviews use reporting guidelines instead - this is bad![@costa2011]

@@

Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: @gwet2008; @wongpakaran2013]

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.

<!--- Cross check this with the actual numbers included --->

@@

One particularly interesting meta-bias potentially applicable in this review is the definition

@@

### Open data sharing {#sys-rev-open-data}

<!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->

@@

__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic. Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.

### 2021-04-12 05-Chp-CPRD-Analysis.Rmd
End of day: -3686

@@

## Aims

In this

@@

@@

@@

@@

@@

Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change. This is problematic when the descision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the inital treatment decision, as is likely to be the case for a range of covariates included in the model. For example:

@@

However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should received a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months. [Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.]

@@

**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c]

@@

As part of our exploration of the unexpected results,

]

@@

@@

Study was reported in line with the [CHECK] reporting guidelines, and

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
```

@@

## Lay summary

The CPR

## Introduction

Lack of evidence for the association of statins on vascular dementia risk

@@

### Data source

The Clinical Practice Research Datalink (CPRD) is a large, population-based, electronic health record database.[@herrett2015] It contains the primary care records for

Originally termed the GPRD (General Practice Research Database),

The

Data completeness and collection of certain disease are heavily influenced by exercises that reward doctors for capturing certain diagnoses, such as the Quality and Outcomes Framework. However, these drives can oftern have unintended consequences [@liu2019]

@@

_Note: If protocol was written by Venexia, how do I reference this?_

@@

<!--- Need a lot more here - see other thesis for example of how covariates are described --->

@@

$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$

where:

* $t$ is the survival time;
* $h(t)$ is the hazard function; and
* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.

As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.

__Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__

Hazard rations are

Test for non-proportionality are therefore very important, as models which fail

Problems with testing for non-proportional hazards when

<!----------------------------------------------------------------------------->
(ref:cprd-dag-1-cap) __Directed acyclic graph showing assumed relationship between exposure and covariate:__

(ref:cprd-dag-1-scap) Directed acyclic graph showing assumed relationship between exposure and covariate

```{r cprd-dag-1, echo = FALSE, results="asis", fig.cap='(ref:cprd-dag-1-cap)', out.width='100%', fig.scap='(ref:cprd-dag-1-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
```
<!----------------------------------------------------------------------------->

@@

Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change. This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model. For example:

@@

However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.

<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should. -->

@@

**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This highlights a particular challenge in comparing research across different time-periods and coding systems. Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.

@@

As part of my exploration of the unexpected results, I attempted to replicate the analyses of another paper that used a different approach to

Having contacted the authors to address these concerns, it was noted that

Propensity scores are based on a range of baseline variables, and provide an estimates of the

They used propensity scores to attempt to matcch patients equally likely to recieve the vaccine

In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared. Fortunately, the authors kindly shared their

<!--- Show comparison of code lists here --->

<!----------------------------------------------------------------------------->
``` {r smeeth-comparison-setup, results="hide", message=FALSE}
```

```{r smeeth-comparison-table, message=FALSE, results="asis"}
```
<!----------------------------------------------------------------------------->

@@

### Coding quality in the CPRD

Lots of things influence prevalence: historic trends, availability of good codes

There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013]

@@

This study was reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->

Reporting
